Untitled

### 2025-02-25 script/r/draft.Rmd
elevation code

@@

```{r}
library(terra)

@@

>>>>

```{r packages, echo=FALSE, }
library(haven)
library(dplyr)
select <- dplyr::select
library(magrittr)
library(stringr)
library(geosphere)
library(purrr)
library(kableExtra)
library(tidyr)
library(readxl)
library(sf)
library(exactextractr)
library(raster)
library(rgdal)
library(ncdf4)
library(terra)
```

#Levels

```{r}
folder_path <- "data/data_raw/gadm"

files <- list.files(folder_path, full.names = TRUE)

levels <- data.frame(file = files) %>%
  mutate(country = str_extract(file, "(?<=_)[A-Z]{3}(?=_\\d)"),
         level = as.integer(str_extract(file, "(?<=_)[0-9]+(?=\\.shp$)"))) %>%
  arrange(country, desc(level)) %>%
  distinct(country, .keep_all = TRUE)

levels %<>%
  group_by(country) %>%
  summarise(levels_nb = first(level))

print(levels, n=40)
```

#Adm setup

```{r}
cty_adm1 <- levels%>%
  filter(levels_nb>=1)%>%
  pull(country)

cty_adm2 <- levels%>%
  filter(levels_nb>=2)%>%
  pull(country)

cty_adm3 <- levels%>%
  filter(levels_nb>=3)%>%
  pull(country)

cty_adm4 <- levels%>%
  filter(levels_nb>=4)%>%
  pull(country)
```

@@

@@

```{r}
tiff_file <- "data/data_raw/geography/elevation/elevation.tif"

elevation_wgs84 <- rast(tiff_file)

print(elevation_wgs84)

plot(elevation_wgs84, main = "Elevation Map", col = terrain.colors(100), breaks = seq(-1000, 3000, by = 100))

elevation_r5_adm1 <- data.frame()

  if (!identical(crs(elevation_wgs84), crs(country_shp))) {
    country_shp <- project(country_shp, crs(elevation_wgs84))
  }

  elevation_wgs84_cropped <- crop(elevation_wgs84, country_shp)
  elevation_wgs84_masked <- mask(elevation_wgs84_cropped, country_shp)

  elevation_adm1 <- exactextractr::exact_extract(elevation_wgs84_masked, regions, 'mean')

  regions$elevation_adm1 <- elevation_adm1
  regions_df <- regions %>%
    as.data.frame() %>%
    rename(iso = GID_0) %>%
    select(iso, NAME_1, elevation_adm1) %>%
    mutate(round = 5)

  elevation_r5_adm1 <- rbind(elevation_r5_adm1, regions_df)
}

elevation_r5_adm1 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(elevation_r5_adm1))

saveRDS(elevation_r5_adm1, file="data/data_rds/geo_ctrl/elevation_r5_adm1.rds")

elevation_r5_adm2 <- data.frame()

  if (!identical(crs(elevation_wgs84), crs(country_shp))) {
    country_shp <- project(country_shp, crs(elevation_wgs84))
  }

  elevation_wgs84_cropped <- crop(elevation_wgs84, country_shp)
  elevation_wgs84_masked <- mask(elevation_wgs84_cropped, country_shp)

  elevation_adm2 <- exactextractr::exact_extract(elevation_wgs84_masked, regions, 'mean')

  regions$elevation_adm2 <- elevation_adm2
  regions_df <- regions %>%
    as.data.frame() %>%
    rename(iso = GID_0) %>%
    select(iso, NAME_2, elevation_adm2) %>%
    mutate(round = 5)

  elevation_r5_adm2 <- rbind(elevation_r5_adm2, regions_df)
}

elevation_r5_adm2 %<>%
  mutate(across(everything(), ~ ifelse(is.nan(.), NA, .)))

print(glimpse(elevation_r5_adm2))

saveRDS(elevation_r5_adm2, file="data/data_rds/geo_ctrl/elevation_r5_adm2.rds")
```
